---
title: "Hantz_Angrand_Assignment5"
author: "Hantz Angrand"
date: "September 29, 2018"
output:
  html_document:
    df_print: paged
---

```{r}
delay<-read.csv("C:/Users/hangr/Documents/Acquisition and data management/Arrivals.csv", header=TRUE)
delay
```

The dataset has 20 records and 7 variables.  We have airlines, the status of the airlines going to 5 cities.Our goal is to compare the arrival delays for the two airlines.

```{r}
#Load the libraries
library(dplyr)
library(tidyr)

```

```{r}
#names the columns
names(delay)[1]<-"Airlines"
names(delay)[2]<-"Status"
delay
```
```{r}
#Remove NA
delay<-delay %>%
  filter(!is.na(Phoenix))

delay
  
```
```{r}
#Fill out missing Airlines Value

delay$Airlines<-as.character(delay$Airlines)
delay$Airlines[delay$Airlines=='']<-c("Alaska", "AM West")
delay
```
##Gather city column and transform it
```{r}
delay_trans<-tidyr::gather(delay,"City", "Count",3:7)
delay_trans
```
##Spresd status so that they become a value
```{r}
delay_trans2<-tidyr::spread(delay_trans,Status, Count)
delay_trans2
```

##Graphof delayed Flight
```{r}
#Upload ggplot library
library(ggplot2)
```

```{r}
#Plot of delayed airlines
ggplot(filter(delay_trans,Status=="Delay"),aes(City,Count, color=Airlines))+geom_point(size=3)+ggtitle("Delayed Flight")+ylab("Number of Delayed Flights")

```
##Comparing the arrivals delay for the two airlines
```{r}
sum_delay<-delay_trans2 %>% dplyr::group_by(Airlines) %>%
  dplyr::summarise(max=max(Delay),
                   min=min(Delay),
                   avg=mean(Delay),
                   SD=sd(Delay),
                   IQR=IQR(Delay))
sum_delay
```
##Conclusion
AM West is most likely to be delayed than Alaska
