---
title: "Hantz_Angrand_Acquisition_HW9"
author: "Hantz Angrand"
date: "October 27, 2018"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The New York Times web site provides a rich set of APIs, as described here:  http://developer.nytimes.com/docs You'll need to start by signing up for an API key. Your task is to choose one of the New York Times APIs, construct an interface in R to read in the JSON data, and transform it to an R dataframe

#Step1 Load Libraries
```{r}
library(httr)
library(jsonlite)
library(stringr)
library(dplyr)

```

Get New York Timeslist  best Seller of harcover fiction APi
```{r}
url = "https://api.nytimes.com/svc/books/v3/lists.json?list=hardcover-fiction&api-key=2ef725a076f148dd868c378cac2f1c72"
books_api<-GET(url)
```


#Step2 Convert into a Dataframe

```{r}
#JSON file
books_parsed<-fromJSON(content(books_api, "text"))
books_parsed
```


```{r}
#Get only the results
df<-data.frame(books_parsed$results)
head(df)
```
```{r}
#From the results get the books details in a table
library(kableExtra)
kable(df$book_details)
```



```{r}
#Print all the best sellers books 
for (i in 1:15){
print(df$book_details[i])
}
```








