---
title: "Hantz_Angrand_Project1"
author: "Hantz Angrand"
date: "September 22, 2018"
output:
  html_document:
    df_print: paged
---
##Project Statement
n this project, you're given a text file with chess tournament results where the information has some structure. Your job is to create an R Markdown file that generates a .CSV file (that could for example be imported into a SQL database) with the following information for all of the players: Player's Name, Player's State, Total Number of Points, Player's Pre-Rating, and Average Pre Chess Rating of Opponents

#First Upload libraries needed for the project
```{r}
library(stringr)
```

#Upload the files from my computer
```{r}
source_data<-read.csv("C:/Users/hangr/Documents/Acquisition and data management/tournamentinfo.txt")
head(source_data)
```

##Cleaning the datasets
```{r}
#First remove separators
rem_sep<-str_detect(source_data,"\\-----")
src_data<-source_data[!rem_sep]
#Remove headers
src_data<-src_data[-c(1:2),]
src_data<-str_split(src_data,"\\|")
```

```{r}
#extract names of all players
ext_names<-str_extract_all(src_data,"[[:alpha:]-?[:alpha:] ?]{2,}")
loc<-str_detect(unlist(ext_names),"[[:alpha:]]{3,}")
player_names<-unlist(ext_names)[loc]
head(player_names)
```

```{r}
#Get State of origin
state_loc<-str_detect(unlist(ext_names),"[[:alpha:]]{2,}")
get_state<-unlist(ext_names)[(state_loc)&(!loc)]
head(get_state)
```

```{r}
#Get Point per games
pts_data<-str_extract_all(src_data,"\\d{1,}+\\.?.?")
pts_location<-str_detect(unlist(pts_data),"\\d\\.\\d")
pts<-unlist(pts_data)[(pts_location)]
head(pts)
```

```{r}
#Get pre_ratings and post_ratings
#Extract pre ratings
rating_data<-str_extract_all(src_data,"(( \\:)|(\\>))?.?\\d{1,}P*\\.?")

pre_location<-str_detect(unlist(rating_data),"\\b\\d{3,4}P?\\b")
post_location<-str_detect(unlist(rating_data),"\\>.?\\b\\d{3,4}P?\\b")
pre_rating<-unlist(rating_data)[(pre_location)&(!post_location)]
pre_rating<-str_replace_all(pre_rating,"P","")
post_rating<-unlist(rating_data)[post_location]
post_rating<-str_replace_all(post_rating,"([>P])","")
head(pre_rating)
```
```{r}
head(post_rating)
```
```{r}
#Get Games played
game_data<-str_extract_all(src_data,"[[:alpha:]]...\\d{1,2}")
game_data<-str_extract_all(game_data,"\\.?\\d{1,2}")
game_data<-str_replace_all(game_data,"\\b[0]\\b",".")
game<-str_detect(game_data,fixed("."))
game_data<-game_data[!(game)]
head(game_data)
```

```{r}
#Combined all the extract into a data frame
player_rank<-data.frame(player_names,get_state,pts,pre_rating,post_rating)
head(player_rank)
```

```{r}
#Convert pts, pre_rating and post_rating to numeric
player_rank$pts<-as.numeric(as.character(player_rank$pts))
player_rank$pre_rating<-as.numeric(as.character(player_rank$pre_rating))
player_rank$post_rating<-as.numeric(as.character(player_rank$post_rating))

head(player_rank)
```

```{r}
result<-array(0)
#Calculate the average
for (i in 1:nrow(player_rank))
{
  result_match<-as.numeric(str_split(unlist(str_extract_all(game_data[i],"\\d{1,2}")), " "))
  result[i]<-mean(player_rank[result_match,colnames(player_rank)=="pre_rating"])
};
player_rank$avg_rating<-result
head(player_rank)
```
##Write the output to CSV file
```{r}
write.csv(player_rank, "chess_data.csv", row.names=FALSE)
```

